---
title: "A Quick Intro on the point-classifier App"
author: "Filippo Ciceri"
date: "5/4/2020"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## The point-classifier app
### General aim:

The **point-classifier** app was designed to play around with the k-means clustering algorithm.
Let's see how!

## Step one
The first step is to generate some random points. The user can define the amount, the standard deviation along the X and Y axis and the number of clusters. 

```{r, echo = TRUE, fig.dim=.5}
points <- 500
sdX <- 2
sdY <- 2
gY <- 3
gX <- 4

x <- rnorm(points, 1, sdX) + 5*sample(c(1:gX),points,replace=TRUE)
y <- rnorm(points, 1, sdY) + 5*sample(c(1:gY),points,replace=TRUE)
plot(x,y) 
```

## Step two
After generating the points the server identifies the clusters. 

```{r, echo = TRUE, fig.dim=.5}
df <- data.frame(x=x,
                 y=y)
kmeansObj <- kmeans(df,centers=gX*gY)
plot(x=x, y=y, col=kmeansObj$cluster)
points(kmeansObj$centers,pch=3,cex=3,lwd=3)
```

## Try yourself!
### Play around with the sliders and see how clusters are identified.

```{r, echo=TRUE}
print("Thank you!!!")
```

